Supplementary Material for Asymmetry paper

### 2020-07-28 Supplementary/Sup_mat.Rmd
Updated sup mat

---
title: "Supplementary Material for Asymmetry paper"
output: 
  bookdown::pdf_document2:
    #theme: journal
    toc: true
bibliography: ["Literature.bib"]
biblio-style: "apalike"
link-citations: true
---

@@

```{r settings, include = F, echo = F}
knitr::opts_chunk$set(fig.align = "center")
```

```{r setup, include=T, message=F, warning=F, echo= F}
# library 
library(tidybayes)
library(tidyverse)
library(brms)
library(png)
library(grid)
library(gridExtra)
library(psyphy)

@@

```{r drawdistributions, include = T, echo = F, fig.height = 5, fig.cap="_These plots show the various distributions that were fit to each participant. These were then used to draw random samples from in order to simulate participants shifting towards one target._", fig.align = 'center'}
# load("../power/Hoop_size/scratch/sampled_data")
load("../power/Hoop_size/scratch/df_part2")

@@

```{r HDIHoopSize, include = T, echo = F, fig.align = 'center', fig.height = 3, fig.cap="_This figure shows how the 95% HDI around the mean difference for the smallest difference simulated (5%) changed with a larger sample size_"}

@@

```{r HoopSizeSession1, include = T, echo = F, warning = F, fig.asp = .75, fig.cap = "_Each facet shows how a participant's accuracy dropped as a function of distance for both hoop sizes that were used in the experiment. The x-axis has been normalised so that 1 represents the furthest distance tested._"}
beanbagdat %>% 
  mutate(delta = slab/max(slab),
         hoop_size = factor(hoop_size, labels = c("Large", "Small"))) %>% 
  ggplot(aes(delta, acc, colour = hoop_size)) + 
  geom_point() + 
  geom_smooth(method = "glm", 
              method.args = list(family = "binomial"),
              se = F,
              fullrange = T) + 
  facet_wrap(~participant, ncol = 7) + 
  theme_bw() + 
  scale_x_continuous(expression(paste("Hoop Delta (", Delta, ")", sep = "")),
                     breaks = seq(0,1,.5)) + 
  scale_y_continuous("Accuracy", labels = scales::percent_format(accuracy = 1)) + 
  guides(colour = guide_legend("Hoop Size")) +
  theme(strip.text.x = element_blank())

@@

```{r HoopSizeFacets, include=T, echo=F, fig.width = 10, fig.height = 10, fig.cap = "_Each facet of this plot shows were each participant stood on each trial. The x-axis shows the different distances that participants were tested at with 0 being the point at which they were closest 50% from the centre. The y-axis shows the normalised standing position between the Big Hoop and the Small Hoop. _"}
load("../Analyses/Experiment_3_Hoop_size/scratch/df_part2_norm")
df_hoopsize <- norm_dat
rm(norm_dat)

@@

```{r HoopSizePriors, include = F, echo = F, warning = F,  fig.asp = .45, fig.cap="_Prior predictions for the Hoop Size experiment_"}
# need to make a dataset
draws <- HS_draw_post(Hoop_size_priors, model_data)

@@

```{r PltHoopSizeEstimates, include = F, echo = F, fig.asp=.45, fig.cap="_Posterior predictions for the mean standing position._"}
plt_post_hoopsize <- draws$plt_estimates + 
  scale_x_continuous(expression(paste("Normalised ", Delta)),
                     limits = c(0,1),
                     breaks = c(0,.5,1),
                     labels = c("Big Hoop", "Centre", "Small Hoop")) + 
  theme(legend.position = "bottom")
```

@@

``` {r PltHoopSize, include = T, echo = F, fig.asp = .45, fig.cap="_Figure on the left shows the Prior predictions. The figure on the right shows the Posterior predictions once the model had been conditioned on the data_"}
# get legend 
HoopSizeLegend <- g_legend(plt_prior_hoopsize)

@@

```{r TwoThrowSession1, include = 1, echo = 1, warning = F, fig.asp = .75, fig.cap = "_Each facet shows how a participant's accuracy dropped as a function of distance. The x-axis has been normalised so 1 represents the furthest range tested._"}
df_part1 %>% 
  mutate(delta = slab/max(slab)) %>% 
  ggplot(aes(delta, acc)) + 
  geom_point() + 
  geom_smooth(method = "glm",
              method.args = list(family = "binomial"),
              se = F) + 
  scale_y_continuous("Accuracy", labels = scales::percent_format(accuracy = 1)) +
  scale_x_continuous(expression(paste("Hoop Delta (", Delta, ")", sep = ""))) +
  facet_wrap(~participant, ncol = 6) + 
  theme_bw() + 
  theme(strip.text.x = element_blank())

@@

``` {r TwoThrowFacets, include = T, echo = F, fig.width = 10, fig.cap = "_Each facet of this plot shows the stnading position on each trial and condition for each participant. The x-axis shows the different distances that participants were tested at with 0 being the point at which they were closest 50% from the centre. The y-axis shows the normalised standing position (between the centre point and one of the two side hoops)._"}
# process 
df_TwoThrow <- model_data_pos %>% 
  group_by(Participant) %>%
  mutate(temp = as.numeric(as.factor(HoopDelta)),
         slab_measures = factor(temp, labels = c("~90%", "~50% - 1", "~50%", "~50% + 1", "~50% + 2", "~10%"))) %>% 
  select(-temp) %>% 
  ungroup() %>% 
  group_by(slab_measures) %>% 
  mutate(overall_hoop_pos = mean(HoopDelta))

@@

```{r TwoThrowPlts, include = T, echo = F, fig.asp = .45, fig.cap = "_The top panel shows the Prior preditcions for the Two Throw experiment. The bottom panel shows the Posterior predictions for the Two Throw expeirment._"}
# get legend 
TwoThrowLegend <- g_legend(priors_plt)

@@

```{r TwoThrowDifference, include = T, echo = F, fig.asp = .45, fig.cap = "_This figure shows the difference in the estimates for the Two Throw experiment. This is the diffrence between the red and blue distributions see in the Figure `@ref(fig:TwoThrowPlts)` with a bigger number representing the One Throw condition have a larger mean than the Two Throw condition._"}
plt_difference
```

@@

``` {r RewardsSession1, include = T, echo = F, warning = F, fig.asp = .75, fig.cap = "_Each facet shows how accuracy changed over distance for each pariticipant. The x-axis has been normalised with 1 being the furthest_"}
df_part1 %>% 
  mutate(Delta = Slab/max(Slab)) %>%
  ggplot(aes(Delta, Accuracy)) + 
  geom_point() + 
  geom_smooth(method = "glm",
              method.args = list(family = "binomial"),
              se = F,
              colour = "black") +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) + 
  scale_x_continuous(expression(paste("Hoop Delta (", Delta, ")", sep = ""))) + 
  theme_bw() +
  theme(strip.text.x = element_blank()) +
  facet_wrap(~Participant)

@@

``` {r RewardFacets, include = T, echo = F, fig.asp = .75, fig.cap = "_Each facet in this plot shows the decision on a single trial about where to stand and how the participant had opted to split the reward. The x-axis corresponds to the participants chance of success had they stood at the centre with the y-axis showing the normalised standing potision._"}
df_Rewards <- model_data %>%
  group_by(Participant) %>%
  mutate(temp = as.numeric(as.factor(Norm_Delta)),
         slab_measures = factor(temp, labels = c("90%", "75%", "25%", "10%"))) %>% 
  select(-temp) %>% 
  ungroup() %>% 
  group_by(slab_measures) %>% 
  mutate(overall_hoop_pos = mean(Norm_Delta))

@@

```{r PltRewardestimates, echo = F, include = T, warning = F, fig.asp=.45, fig.cap="_This plot shows the posterior distribution of standing positions for the Reward study_"}
grid.arrange(arrangeGrob(plt_RewardPriors + theme(legend.position = "none"), plt_inter + theme(legend.position = "none")), Reward_legend, ncol = 2, widths = c(6,1))
#plt_inter
```

@@

```{r ProbOGData, include=T, echo=F, fig.asp=.45, fig.cap="_Boxplots to show the proportion of trials in which the participants fixated the each box by Condition and Distance type_"}
plt_data <- df_resample %>%  
  ungroup() %>% 
  group_by(Participant, Condition, Dist_type) %>% 
  mutate(centre = ifelse(box_type == "Centre", 1, 0),
         ML = ifelse(box_type == "Most", 1, 0),
         LL = ifelse(box_type == "Least", 1, 0),
         n = n()) %>%
  summarise(centre = mean(centre),
            ML = mean(ML),
            LL = mean(LL)) %>% 
  gather(centre:LL,
         key = "prop_type",
         value = "proportion") %>%
  mutate(prop_type = factor(prop_type, c("centre", "ML", "LL"),
                            labels = c("Centre", "Most Likely", "Least Likely"))) %>% 
  ggplot(aes(Dist_type, proportion,
             fill = Condition,
             colour = Condition)) + 
  geom_boxplot(alpha = .3) + 
  geom_point(alpha = .3, position = position_jitterdodge(.1)) +
  facet_wrap(~prop_type) +
  see::scale_color_flat() +
  see::scale_fill_flat() +
  theme_bw() +
  scale_x_discrete("Distance Type") +
  theme(axis.title.y = element_blank())
plt_data
```

@@

```{r ProbPowerPlots, include = T, echo = F, fig.asp=.45, fig.cap="_Plot to show how the 95% HDI of the estimated difference in fixations to the most likely box changed with an increase in participants_"}
# maybe just the hdi stuff?
# do I want to rerun the sim with dist type added in?
plt_resampling <- df_sample %>% 
  spread(Condition, 
         Most) %>% 
  mutate(diff = Bias - Symmetric) %>% 
  group_by(n_sub) %>% 
  summarise(mu = mean(diff),
            lower = hdi(diff)[1],
            upper = hdi(diff)[2]) %>% 
  ggplot(aes(n_sub, mu)) + 
  geom_line() + 
  geom_ribbon(aes(ymin = lower,
                  ymax = upper),
              alpha = .3) +
  theme_bw() + 
  scale_x_continuous("Sample Size") + 
  scale_y_continuous("Difference in fixations to more \n likely side (Bias - Symmetric)")

@@

```{r ProbSession1, include=T, echo=F, fig.asp=.45, fig.cap="_The sequence for every trial in Session 1_"}

plt_fig1 <- readPNG("../Figures/Experiment_4_Prob/Part1_Trial.png")
grid.raster(plt_fig1)

@@

```{r ProbSession2, include=T, echo=F, fig.asp=.45, fig.cap="_The sequence for every trial in Session 2_"}

@@

## Results
```{r ProbProp, include = T, echo = F, fig.asp=.45, fig.cap="_These boxplots show the proportion of the time that participants fixated the centre (left panel), most-likely (central panel) and least-likely (right panel) box. In the _Bias_ condition, 'most likely' was the box with and 80% probability of containing the target. In the _Symmetric_ condition, 'most-likely' was whichever side box a given participant had fixated the most. The Close and Far distinction is baseed on when participants should swith from fixating the central box to the side box. Note that for some participants, expected performance differences between the Centre and Side strategies for the closest separation was negligible. However, all participants should have fixated the Side boxes in the Far condition, where the performance advantage of doing so was substantial._"}

@@

```{r ProbExpAcc, include = T, echo = F, fig.asp = .45, fig.cap = "_These show the expected accuracy for each participant (black lines) plotted against $\\Delta$. The different shaded regions show the minimum (orange) and maximum (green) expected accuracy rates for all participants. $\\Delta$ is the separations at which each participant was tested rescaled to be between 0 and 1_"}
plt_prop_expAcc <- readPNG("../Figures/Experiment_4_Prob/region_performance.png")
grid.raster(plt_prop_expAcc)
```

@@

### Session 1 Accuracy 
```{r probSession1, include = T, echo = F, warning = F, fig.asp = .75, fig.cap = "_This figure shows the rate at which participants correctly identified the target letter presented within a box placed some distance from the centre with the lines showing a logistic regression on these data._"}
# load in part 1 data 
load("../Analyses/Experiment_4_Prob/scratch/new_data/Part_1_data_nar")

@@

```{r ProbPriors, include = T, echo = T, message = F, warning = F, results = "hide", cache = TRUE}
ProbPriors_model <- brm(Ml_fix ~ (bias_type + dist_type)^2 + (dist_type * bias_type|participant),
                        data = df_model,
                        family = "bernoulli",
                        prior = Rewards_priors,
                        chains = 1,
                        iter =   n_iter,
                        warmup = n_warmup,
                        sample_prior = "only")
```

@@

```{r ProbPriorsPlt, echo = F, fig.cap="_Prior Predictive checks for the Probability matching experiment_"}
gridExtra::grid.arrange(plt_ProbPrior_meDist, bottom, heights = c(2, 4))
```

@@

```{r ProbModelOutputs, include = T, echo = F, fig.cap = "_Posterior predictions for the probability matching experiment_"}
gridExtra::grid.arrange(plt_me_Dist, bottom,  ncol = 1, heights = c(2,4))
```

@@

>>>>

---
title: "Supplementary Material for Asymmetry paper"
output: 
  bookdown::pdf_document2:
    #theme: journal
    toc: true
    keep_tex: false
bibliography: ["Literature.bib"]
biblio-style: "apalike"
link-citations: true
---

@@

```{r setup, include=T, message=F, warning=F, echo= F}
knitr::opts_chunk$set(fig.align = "center")
# library 
library(tidybayes)
library(tidyverse)
library(brms)
library(png)
library(grid)
library(gridExtra)
library(psyphy)

@@

```{r drawdistributions, include = T, echo = F, fig.height = 5, fig.cap="These plots show the various distributions that were fit to each participant. These were then used to draw random samples from in order to simulate participants shifting towards one target."}
# load("../power/Hoop_size/scratch/sampled_data")
load("../power/Hoop_size/scratch/df_part2")

@@

```{r HDIHoopSize, include = T, echo = F, warning = F, fig.height = 3, fig.cap="This figure shows how the 95\\% HDI around the mean difference for the smallest difference simulated (5\\%) changed with a larger sample size"}

@@

```{r HoopSizeSession1, echo = F, warning = F, fig.asp = .75, fig.cap = "Each facet shows how a participant's accuracy dropped as a function of distance for both hoop sizes that were used in the experiment. The x-axis has been normalised so that 1 represents the furthest distance tested."}
beanbagdat %>% 
  mutate(delta = slab/max(slab),
         hoop_size = factor(hoop_size, labels = c("Large", "Small"))) %>% 
  ggplot(aes(delta, acc, colour = hoop_size)) + 
  geom_point() + 
  geom_smooth(method = "glm", 
              method.args = list(family = "binomial"),
              se = F,
              fullrange = T) + 
  facet_wrap(~participant, ncol = 7) + 
  theme_bw() + 
  scale_x_continuous(expression(paste("Hoop Delta (", Delta, ")", sep = "")),
                     breaks = seq(0,1,.5)) + 
  scale_y_continuous("Accuracy", labels = scales::percent_format(accuracy = 1)) + 
  guides(colour = guide_legend("Hoop Size")) +
  theme(strip.text.x = element_blank())

@@

```{r HoopSizeFacets, include=T, echo=F, fig.width = 10, fig.height = 10, fig.cap = "Each facet of this plot shows were each participant stood on each trial. The x-axis shows the different distances that participants were tested at with 0 being the point at which they were closest 50\\% from the centre. The y-axis shows the normalised standing position between the Big Hoop and the Small Hoop."}
load("../Analyses/Experiment_3_Hoop_size/scratch/df_part2_norm")
df_hoopsize <- norm_dat
rm(norm_dat)

@@

```{r HoopSizePriors, include = F, echo = F, warning = F,  fig.asp = .45, fig.cap="Prior predictions for the Hoop Size experiment"}
# need to make a dataset
draws <- HS_draw_post(Hoop_size_priors, model_data)

@@

```{r PltHoopSizeEstimates, include = F, echo = F, fig.asp=.45, fig.cap="Posterior predictions for the mean standing position."}
plt_post_hoopsize <- draws$plt_estimates + 
  scale_x_continuous(expression(paste("Normalised ", Delta)),
                     limits = c(0,1),
                     breaks = c(0,.5,1),
                     labels = c("Big Hoop", "Centre", "Small Hoop")) + 
  theme(legend.position = "bottom")
```

@@

``` {r PltHoopSize, include = T, echo = F, fig.asp = .45, fig.cap="Figure on the left shows the Prior predictions. The figure on the right shows the Posterior predictions once the model had been conditioned on the data"}
# get legend 
HoopSizeLegend <- g_legend(plt_prior_hoopsize)

@@

```{r TwoThrowSession1, include = 1, echo = 1, warning = F, fig.asp = .75, fig.cap = "Each facet shows how a participant's accuracy dropped as a function of distance. The x-axis has been normalised so 1 represents the furthest range tested."}
df_part1 %>% 
  mutate(delta = slab/max(slab)) %>% 
  ggplot(aes(delta, acc)) + 
  geom_point() + 
  geom_smooth(method = "glm",
              method.args = list(family = "binomial"),
              se = F) + 
  scale_y_continuous("Accuracy", labels = scales::percent_format(accuracy = 1)) +
  scale_x_continuous(expression(paste("Hoop Delta (", Delta, ")", sep = ""))) +
  facet_wrap(~participant, ncol = 6) + 
  theme_bw() + 
  theme(strip.text.x = element_blank())

@@

``` {r TwoThrowFacets, include = T, echo = F, fig.width = 10, fig.cap = "Each facet of this plot shows the stnading position on each trial and condition for each participant. The x-axis shows the different distances that participants were tested at with 0 being the point at which they were closest 50\\% from the centre. The y-axis shows the normalised standing position (between the centre point and one of the two side hoops)."}
# process 
df_TwoThrow <- model_data_pos %>% 
  group_by(Participant) %>%
  mutate(temp = as.numeric(as.factor(HoopDelta)),
         slab_measures = factor(temp, labels = c("~90%", "~50% - 1", "~50%", "~50% + 1", "~50% + 2", "~10%"))) %>% 
  select(-temp) %>% 
  ungroup() %>% 
  group_by(slab_measures) %>% 
  mutate(overall_hoop_pos = mean(HoopDelta))

@@

```{r TwoThrowPlts, include = T, echo = F, fig.asp = .45, fig.cap = "The top panel shows the Prior preditcions for the Two Throw experiment. The bottom panel shows the Posterior predictions for the Two Throw expeirment."}
# get legend 
TwoThrowLegend <- g_legend(priors_plt)

@@

```{r TwoThrowDifference, include = T, echo = F, fig.asp = .45, fig.cap = "This figure shows the difference in the estimates for the Two Throw experiment. This is the diffrence between the red and blue distributions see in the Figure `@ref(fig:TwoThrowPlts)` with a bigger number representing the One Throw condition have a larger mean than the Two Throw condition."}
plt_difference
```

@@

``` {r RewardsSession1, include = T, echo = F, warning = F, fig.asp = .75, fig.cap = "Each facet shows how accuracy changed over distance for each pariticipant. The x-axis has been normalised with 1 being the furthest"}
df_part1 %>% 
  mutate(Delta = Slab/max(Slab)) %>%
  ggplot(aes(Delta, Accuracy)) + 
  geom_point() + 
  geom_smooth(method = "glm",
              method.args = list(family = "binomial"),
              se = F,
              colour = "black") +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1)) + 
  scale_x_continuous(expression(paste("Hoop Delta (", Delta, ")", sep = ""))) + 
  theme_bw() +
  theme(strip.text.x = element_blank()) +
  facet_wrap(~Participant)

@@

``` {r RewardFacets, include = T, echo = F, fig.asp = .75, fig.cap = "Each facet in this plot shows the decision on a single trial about where to stand and how the participant had opted to split the reward. The x-axis corresponds to the participants chance of success had they stood at the centre with the y-axis showing the normalised standing potision."}
df_Rewards <- model_data %>%
  group_by(Participant) %>%
  mutate(temp = as.numeric(as.factor(Norm_Delta)),
         slab_measures = factor(temp, labels = c("90%", "75%", "25%", "10%"))) %>% 
  select(-temp) %>% 
  ungroup() %>% 
  group_by(slab_measures) %>% 
  mutate(overall_hoop_pos = mean(Norm_Delta))

@@

```{r PltRewardestimates, echo = F, include = T, warning = F, fig.asp=.45, fig.cap="This plot shows the posterior distribution of standing positions for the Reward study"}
grid.arrange(arrangeGrob(plt_RewardPriors + theme(legend.position = "none"), plt_inter + theme(legend.position = "none")), Reward_legend, ncol = 2, widths = c(6,1))
#plt_inter
```

@@

```{r ProbOGData, include=T, echo=F, fig.asp=.45, fig.cap="Boxplots to show the proportion of trials in which the participants fixated the each box by Condition and Distance type"}
plt_data <- df_resample %>%  
  ungroup() %>% 
  group_by(Participant, Condition, Dist_type) %>% 
  mutate(centre = ifelse(box_type == "Centre", 1, 0),
         ML = ifelse(box_type == "Most", 1, 0),
         LL = ifelse(box_type == "Least", 1, 0),
         n = n()) %>%
  summarise(centre = mean(centre),
            ML = mean(ML),
            LL = mean(LL)) %>% 
  gather(centre:LL,
         key = "prop_type",
         value = "proportion") %>%
  mutate(prop_type = factor(prop_type, c("centre", "ML", "LL"),
                            labels = c("Centre", "Most Likely", "Least Likely"))) %>% 
  ggplot(aes(Dist_type, proportion,
             fill = Condition,
             colour = Condition)) + 
  geom_boxplot(alpha = .3) + 
  geom_point(alpha = .3, position = position_jitterdodge(.1)) +
  facet_wrap(~prop_type) +
  see::scale_color_flat() +
  see::scale_fill_flat() +
  theme_bw() +
  scale_x_discrete("Distance Type") +
  theme(axis.title.y = element_blank())
plt_data
```

@@

```{r ProbPowerPlots, include = T, echo = F, fig.asp=.45, fig.cap="Plot to show how the 95\\% HDI of the estimated difference in fixations to the most likely box changed with an increase in participants"}
# maybe just the hdi stuff?
# do I want to rerun the sim with dist type added in?
plt_resampling <- df_sample %>% 
  spread(Condition, 
         Most) %>% 
  mutate(diff = Bias - Symmetric) %>% 
  group_by(n_sub) %>% 
  summarise(mu = mean(diff),
            lower = hdi(diff)[1],
            upper = hdi(diff)[2]) %>% 
  ggplot(aes(n_sub, mu)) + 
  geom_line() + 
  geom_ribbon(aes(ymin = lower,
                  ymax = upper),
              alpha = .3) +
  theme_bw() + 
  scale_x_continuous("Sample Size") + 
  scale_y_continuous("Difference in fixations to more \n likely side (Bias - Symmetric)")

@@

```{r ProbPart1, include=T, echo=F, fig.asp=.45, fig.cap="The sequence for every trial in Session 1"}

plt_session1Prob <- readPNG("../Figures/Experiment_4_Prob/Part2_Trial.png")
grid.raster(plt_session1Prob)

@@

```{r ProbSession2, include=T, echo=F, fig.asp=.45, fig.cap="The sequence for every trial in Session 2"}

@@

## Results
```{r ProbProp, include = T, echo = F, fig.asp=.45, fig.cap="These boxplots show the proportion of the time that participants fixated the centre (left panel), most-likely (central panel) and least-likely (right panel) box. In the Bias condition, most likely was the box with and 80\\% probability of containing the target. In the Symmetric condition, most-likely was whichever side box a given participant had fixated the most. The Close and Far distinction is baseed on when participants should swith from fixating the central box to the side box. Note that for some participants, expected performance differences between the Centre and Side strategies for the closest separation was negligible. However, all participants should have fixated the Side boxes in the Far condition, where the performance advantage of doing so was substantial."}

@@

```{r ProbExpAcc, include = T, echo = F, fig.asp = .45, fig.cap = "These show the expected accuracy for each participant (black lines) plotted against $\\Delta$. The different shaded regions show the minimum (orange) and maximum (green) expected accuracy rates for all participants. $\\Delta$ is the separations at which each participant was tested rescaled to be between 0 and 1"}
plt_prop_expAcc <- readPNG("../Figures/Experiment_4_Prob/region_performance.png")
grid.raster(plt_prop_expAcc)
```

@@

### Session 1 Accuracy 
```{r probSession1, include = T, echo = F, warning = F, fig.asp = .75, fig.cap = "This figure shows the rate at which participants correctly identified the target letter presented within a box placed some distance from the centre with the lines showing a logistic regression on these data."}
# load in part 1 data 
load("../Analyses/Experiment_4_Prob/scratch/new_data/Part_1_data_nar")

@@

```{r ProbPriors, include = F, echo = F, message = F, warning = F, results = "hide", cache = TRUE}
ProbPriors_model <- brm(Ml_fix ~ (bias_type + dist_type)^2 + (dist_type * bias_type|participant),
                        data = df_model,
                        family = "bernoulli",
                        prior = Rewards_priors,
                        chains = 1,
                        iter =   n_iter,
                        warmup = n_warmup,
                        sample_prior = "only")
```

@@

```{r ProbPriorsPlt, echo = F, fig.cap="Prior Predictive checks for the Probability matching experiment"}
gridExtra::grid.arrange(plt_ProbPrior_meDist, bottom, heights = c(2, 4))
```

@@

```{r ProbModelOutputs, include = T, echo = F, fig.cap = "Posterior predictions for the probability matching experiment"}
gridExtra::grid.arrange(plt_me_Dist, bottom,  ncol = 1, heights = c(2,4))
```

@@

\newpage
